---
title: "Analyses"
bibliography: references.bib
date: "Last compiled on `r format(Sys.time(), '%B, %Y')`"
output: 
  html_document:
    css: tweaks.css
    toc:  true
    toc_float: true
    number_sections: false
    toc_depth: 1
    code_folding: show
    code_download: yes
---
  
```{r echo=FALSE, warning=FALSE, results='hide', message=FALSE}
library(knitr)
library(dplyr)
knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = FALSE, cache=TRUE, class.source=c("test2"), class.output=c("test2"))
options(width = 100)
rgl::setupKnitr()
options(knitr.kable.NA = '')


colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }
```


```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```



---  
  
  
  
# Tie maintenance?
```{r, class.source = 'fold-hide'}
rm(list=ls())

load("tie_maintenance.RData")

tab <- psych::describe(df$survive)
tab<-tab[,c(8,9,3)]
rownames(tab) <- "tie survived? (1=yes, 0=no)"

knitr::kable(tab, digits=3, "html", caption="Tie maintenance among first-year students over approximately one year$^a$") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>%
  kableExtra::add_footnote("690 alters, nested in 90 students.", notation="alphabet")

 

```
<br>

50 percent of all alters was maintained.

For comparison:

- Marin and Hamption (2019)
- Feld (1996)
- Fisher and Offer (2020)


<br>


----

# Political homophily?

Does similarity in political orientation predict tie maintenance?

<br>

- The more "extreme" egos political attitude (be it left or right), the higher the probability of maintaining ties (Model 6: $OR_{ego.pol}$=1.26, *CI*=[1.03 – 1.55]).

- A positive but not significant alter-effect of political attitude (Model 3: $OR_{alter.pol}$=1.09, *CI*=[0.93 – 1.28]).

- Dissimilarity in political opinion (here, the absolute difference between ego and alter), decreases the probability of tie maintenance (Model 6: $OR_{ego-alter.diff.pol}$=0.87, *CI*=[0.76 – 1.00]).

- Other dyadic features: age *dis*similarity predicts tie maintenance (probably due to kin often being older). Stronger ties, here in terms of contact frequency and emotional connection, are more stable.


```{r,class.source = 'fold-hide', eval=F}
library(lme4) # fitting random effects models
library(sjPlot) # plot functions

# let's explore the role of political orientation similarity in predicting tie maintenance.
# make ego and alter political orientation from -5 tot +5, take absolute score
df$alter_pol_abs <- ifelse(df$alter_pol>5, as.numeric(df$alter_pol)-5,
                                  ifelse(df$alter_pol<5, abs(as.numeric(df$alter_pol)-5), 0))  
df$ego_pol_abs <- ifelse(df$ego_pol>5, as.numeric(df$ego_pol)-5,
                           ifelse(df$ego_pol<5, abs(as.numeric(df$ego_pol)-5), 0))  

# dichotomize gender (ref.=male)
df$ego_gender <- ifelse(df$ego_gender==2, 1, df$ego_gender)

# empty model
m1 <- glmer ( survive ~ 1 + (1 | ego), data=df, family = "binomial")

# build increasingly complex model
# basic ego-demographics
m2 <- glmer ( survive ~ ego_gender + ego_age + (1 | ego), data=df, family = "binomial") 
# psychological attributes (loneliness, extraversion)
m3 <- glmer ( survive ~ ego_gender + ego_age + loneliness + extraversion + (1 | ego), data=df, family = "binomial") 
# financial restrictions
m4 <- glmer ( survive ~ ego_gender + ego_age + loneliness + extraversion + fin_restr + (1 | ego), data=df, family = "binomial") 
# add ego political orientation
m5 <- glmer ( survive ~ ego_gender + ego_age + loneliness + extraversion + fin_restr + ego_pol_abs + (1 | ego), data=df, family = "binomial") 

# add alter orientation 
m6 <- glmer ( survive ~ ego_gender + ego_age + loneliness + extraversion + ego_pol_abs +
               alter_pol_abs + (1 | ego), data=df, family = "binomial") 
# and similarity (difference score)
m7 <- glmer ( survive ~ ego_gender + ego_age + loneliness + extraversion + ego_pol_abs +
               dif_pol + (1 | ego), data=df, family = "binomial")
# add other dyadic similarity measures
m8 <- glmer ( survive ~ ego_gender + ego_age + loneliness + extraversion + ego_pol_abs +
               dif_pol + sim_educ + same_gender + dif_age + (1 | ego), data=df, family = "binomial")
# add dyadic feature indicating tie strength
m9 <- glmer ( survive ~ ego_gender + ego_age + loneliness + extraversion + ego_pol_abs +
               dif_pol + sim_educ + same_gender + dif_age  +  frequency + closeness + (1 | ego), data=df, family = "binomial")

# last, add dynamic contextual variables,
# indicating whether ego experienced a residential transition over the academic year / whether ego became member of new
# (formal) organizations after transitioning to uni. 
m10 <- glmer ( survive ~ ego_gender + ego_age + loneliness + extraversion + ego_pol_abs +
               dif_pol + sim_educ + same_gender + dif_age  + frequency + closeness + housing_change + joined_org + (1 | ego), data=df, family = "binomial")
# pred labels
pl <- c(
  `(Intercept)` = "(Intercept)",
  ego_pol_abs = "Ego political orientation (0-5)",
  ego_gender = "Ego gender (ref. = male)",
  ego_age = "Ego age (in years)",
  extraversion = "Extraversion",
  loneliness = "Loneliness",
  fin_restr = "Financial restrictions",
  alter_pol_abs = "Alter political orientation (0-5)",
  alter_educ = "Alter education",
  dif_pol = "Ego-alter diff. pol. orientation",
  dif_age = "Ego-alter diff. age",
  sim_educ = "Same education",
  same_gender = "Same gender",
  frequency = "Contact frequency",
  closeness = "Emotional closeness",
  housing_change = "Residential change",
  joined_org = "Joined (formal) organization(s)")

# table
tab_model(m1,m5,m6,m8,m9,m10,
          dv.labels = c("Model 1 (empty)", "Model 2 (ego attributes)", "Model 3 (alter attributes)", "Model 4 (similarity)","Model 5 (dyad covars)", "Model 6 (life events)"),
          p.style="stars",
          title="Table 1. Effects on tie maintenance",
          string.est="OR",
          file="analyses/table1.html",
          pred.labels = pl)

```

```{r, echo=FALSE}
htmltools::includeHTML("analyses/table1.html")
```