---
title: "Data preparation"
bibliography: references.bib
date: "Last compiled on `r format(Sys.time(), '%B, %Y')`"
output: 
  html_document:
    css: tweaks.css
    toc:  true
    toc_float: true
    number_sections: false
    toc_depth: 1
    code_folding: show
    code_download: yes
---

```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test3"))
options(width = 100)
rgl::setupKnitr()


colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }
```


```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```


---  



# tie_maintenance.RData

In the following script, I use waves 1 and 2 of the survey project *Sports & Networks* [Franken et al., -@data2022]. 

In wave 1, we gathered information on the social context of students prior to their transition ot tertiary education, as well as their personal networks at that time. We used 4 name generators (*core discussion network*, and networks consisting of core *study partners*, *best friends*, and *sports partners*), and we assessed the overlap between these networks. In wave 2, in the middle of the academic year, we used similar name generator questions to map these ego-nets. 

Based on these data, I construct a long data-frame (with alters nested in egos) to investigate which alters are maintained in the personal networks of ego. To each ego, relevant individual-level, contextual-level, and network-level predictors are assigned; to each alter, relevant alter and dyadic features are assigned. 

This script uses lists and loops a lot! Maybe not the most efficient, but it gets the job done.

```{r eval=FALSE, class.output="scrol-100"}
#rm(list=ls())
# load in the data of wave 1
data <- read.csv("data/results-survey938243.csv") 
# also data of wave 2
# after all, I want to study tie maintenance
data2 <- read.csv("data/results-survey868275.csv")

# subset respondents that filled out both surveys;
# by matching based on emailadress
data <- data[which(data$email %in% unique(data2$email)),]
#nrow(data) #n=95

# i make a dataframe of alters, with potential duplicates...
df_names <- data.frame(
  p1 = data$egonet1.SQ001.,
  p2 = data$egonet1.SQ002.,
  p3 = data$egonet1.SQ003.,
  p4 = data$egonet1.SQ004.,
  p5 = data$egonet1.SQ005.,
  p6 = data$egonet2.SQ001.,
  p7 = data$egonet2.SQ002.,
  p8 = data$egonet2.SQ003.,
  p9 = data$egonet2.SQ004.,
  p10= data$egonet2.SQ005.,
  p11= data$egonet3.SQ001.,
  p12= data$egonet3.SQ002.,
  p13= data$egonet3.SQ003.,
  p14= data$egonet3.SQ004.,
  p15= data$egonet3.SQ005.,
  p16= data$egonet4.SQ001.,
  p17= data$egonet4.SQ002.,
  p18= data$egonet4.SQ003.,
  p19= data$egonet4.SQ004.,
  p20= data$egonet4.SQ005.)

# i exclude the isolates 
isolates <- which(rowSums(df_names=="")==20) #i.e., 20 empty name fields
df_names <- df_names[-isolates, ]
#nrow(df_names) #n=92

# i also filter these out from our data...
data <- data[-isolates,]

# i make a list of data-frames (per ego) with rows reflecting alters;
# a column indicating the alter number, 1:20
# and 4 columns indicating the name(s) of the particular alter
# after all, an alter could, hypothetically, be listed 4 times, with different
# names
# i also add variables for ego-level characteristics ("constant" over alter);
# and alter- and dyadic features
alterL <- list()
# loop over all egos
for ( i in 1:nrow(df_names)) {
  alterL[[i]] <- data.frame(
    ego_gender = NA,
    ego_educ = NA,
    ego_age = NA,
    ego_pol = NA, 
    alterid = 1:20,
    name1 = NA,
    name2 = NA,
    name3 = NA,
    name4 = NA,
    # alter level
    alter_gender = NA,
    alter_educ = NA,
    alter_age = NA,
    alter_pol = NA,
    # ...
    # dyadic level
    same_gender = NA,
    sim_educ = NA,
    dif_age = NA,
    dif_pol = NA, #similarity in political placement (left-right) of ego and alter
    close = NA,   #emotional closeness
    con_freq = NA,#contact frequency
    tie_dur = NA, #tie duration
    prox = NA     #physical proximity
    # ...
    # @RF... to add: other ego-variables, str. embeddedness, 
    # network-variables (e.g., size,density);
    # context; ideally, dynamic measures, i.e., measures of change in variables
    # pertaining to demographic features (e.g., life events: change of residency etc.)
  )
}

# fill the names based on the names data-frame
for ( i in 1:length(alterL)) {
  alterL[[i]]$name1 <- unlist(df_names[i, ], use.names=F)
}

# replace empty strings with <NA>
for (i in 1:length(alterL)) {
  alterL[[i]]$name1 <- ifelse(alterL[[i]]$name1=="", NA, alterL[[i]]$name1)
}

# a matching matrix allowed ego to match names that referred to the same person.
# unfortunately, in limesurvey, i could not let the number of columns condition
# on the number of alters named in the latest net, so i made 5 separate matrices,
# conditional on netsize.
# i calculate netsize for each net
{
  net1 <- cbind(data$egonet1.SQ001.,data$egonet1.SQ002., data$egonet1.SQ003.,data$egonet1.SQ004., data$egonet1.SQ005.)
  net1 <- ifelse(net1=="", NA, net1)
  ns1 <- vector()
  for (i in 1:nrow(net1)) {
    ns1[i] <- length(net1[i,][which(!is.na(net1[i,]))])
  }
  net2 <- cbind(data$egonet2.SQ001.,data$egonet2.SQ002., data$egonet2.SQ003.,data$egonet2.SQ004., data$egonet2.SQ005.)
  net2 <- ifelse(net2=="", NA, net2)
  ns2 <- vector()
  for (i in 1:nrow(net2)) {
    ns2[i] <- length(net2[i,][which(!is.na(net2[i,]))])
  }
  net3 <- cbind(data$egonet3.SQ001.,data$egonet3.SQ002., data$egonet3.SQ003.,data$egonet3.SQ004., data$egonet3.SQ005.)
  net3 <- ifelse(net3=="", NA, net3)
  ns3 <- vector()
  for (i in 1:nrow(net3)) {
    ns3[i] <- length(net3[i,][which(!is.na(net3[i,]))])
  }
  net4 <- cbind(data$egonet4.SQ001.,data$egonet4.SQ002., data$egonet4.SQ003.,data$egonet4.SQ004., data$egonet4.SQ005.)
  net4 <- ifelse(net4=="", NA, net4)
  ns4 <- vector()
  for (i in 1:nrow(net4)) {
    ns4[i] <- length(net4[i,][which(!is.na(net4[i,]))])
  }
}

# i construct the matching matrices, 1 - 5 (conditional on the ns of the latest net)
# put these in a list
# and list these again, for each respondent
# so a list of lists...
matchingList <- list()
for (i in 1:length(alterL)) { # for ego i
  matchingL <- list()
  # make 5 seperate matching matrices. naturally, only 1 is relevant... but i will select that later.
  matchingL[[1]] <- cbind(data$matching1N1.SQ001_SQ001.[i],data$matching1N1.SQ002_SQ001.[i],data$matching1N1.SQ003_SQ001.[i],data$matching1N1.SQ004_SQ001.[i],data$matching1N1.SQ005_SQ001.[i])
  matchingL[[2]]<- rbind(
    cbind(data$matching1N2.SQ001_SQ001.[i], data$matching1N2.SQ002_SQ001.[i], data$matching1N2.SQ003_SQ001.[i], data$matching1N2.SQ004_SQ001.[i], data$matching1N2.SQ005_SQ001.[i]),
    cbind(data$matching1N2.SQ001_SQ002.[i], data$matching1N2.SQ002_SQ002.[i], data$matching1N2.SQ003_SQ002.[i], data$matching1N2.SQ004_SQ002.[i], data$matching1N2.SQ005_SQ002.[i]))
  matchingL[[3]]<- rbind(
    cbind(data$matching1N3.SQ001_SQ001.[i], data$matching1N3.SQ002_SQ001.[i], data$matching1N3.SQ003_SQ001.[i], data$matching1N3.SQ004_SQ001.[i], data$matching1N3.SQ005_SQ001.[i]),
    cbind(data$matching1N3.SQ001_SQ002.[i], data$matching1N3.SQ002_SQ002.[i], data$matching1N3.SQ003_SQ002.[i], data$matching1N3.SQ004_SQ002.[i], data$matching1N3.SQ005_SQ002.[i]),
    cbind(data$matching1N3.SQ001_SQ003.[i], data$matching1N3.SQ002_SQ003.[i], data$matching1N3.SQ003_SQ003.[i], data$matching1N3.SQ004_SQ003.[i], data$matching1N3.SQ005_SQ003.[i]))
  matchingL[[4]]<- rbind(
    cbind(data$matching1N4.SQ001_SQ001.[i], data$matching1N4.SQ002_SQ001.[i], data$matching1N4.SQ003_SQ001.[i], data$matching1N4.SQ004_SQ001.[i], data$matching1N4.SQ005_SQ001.[i]),
    cbind(data$matching1N4.SQ001_SQ002.[i], data$matching1N4.SQ002_SQ002.[i], data$matching1N4.SQ003_SQ002.[i], data$matching1N4.SQ004_SQ002.[i], data$matching1N4.SQ005_SQ002.[i]),
    cbind(data$matching1N4.SQ001_SQ003.[i], data$matching1N4.SQ002_SQ003.[i], data$matching1N4.SQ003_SQ003.[i], data$matching1N4.SQ004_SQ003.[i], data$matching1N4.SQ005_SQ003.[i]),
    cbind(data$matching1N4.SQ001_SQ004.[i], data$matching1N4.SQ002_SQ004.[i], data$matching1N4.SQ003_SQ004.[i], data$matching1N4.SQ004_SQ004.[i], data$matching1N4.SQ005_SQ004.[i]))
  matchingL[[5]]<- rbind(
    cbind(data$matching1N5.SQ001_SQ001.[i], data$matching1N5.SQ002_SQ001.[i], data$matching1N5.SQ003_SQ001.[i], data$matching1N5.SQ004_SQ001.[i], data$matching1N5.SQ005_SQ001.[i]),
    cbind(data$matching1N5.SQ001_SQ002.[i], data$matching1N5.SQ002_SQ002.[i], data$matching1N5.SQ003_SQ002.[i], data$matching1N5.SQ004_SQ002.[i], data$matching1N5.SQ005_SQ002.[i]),
    cbind(data$matching1N5.SQ001_SQ003.[i], data$matching1N5.SQ002_SQ003.[i], data$matching1N5.SQ003_SQ003.[i], data$matching1N5.SQ004_SQ003.[i], data$matching1N5.SQ005_SQ003.[i]),
    cbind(data$matching1N5.SQ001_SQ004.[i], data$matching1N5.SQ002_SQ004.[i], data$matching1N5.SQ003_SQ004.[i], data$matching1N5.SQ004_SQ004.[i], data$matching1N5.SQ005_SQ004.[i]),
    cbind(data$matching1N5.SQ001_SQ005.[i], data$matching1N5.SQ002_SQ005.[i], data$matching1N5.SQ003_SQ005.[i], data$matching1N5.SQ004_SQ005.[i], data$matching1N5.SQ005_SQ005.[i]))
  matchingList[[i]] <- matchingL
} # so... matchingL[[1]][[5]] is matchingmatrix 5 (i.e., 5 alters named in egonet2) for ego 1

# the combination of the matching matrices and the netsizes for ego allows me to match the names myself.
for (i in 1:length(matchingList)) {     # for ego i
  mL <- matchingList[[i]]               # get the matching list
  ns <- ns2[[i]]                        # get the size of egonet2
  if(ns>0) {                            # if ns=0, no matching was done!
    mm <- as.matrix(mL[[ns]])           # retrieve the corresponding matrix
    matched <- which(mm==1, arr.ind=T)  # retrieve array indices
    net <- net2[i,]
    alterL[[i]]$name2[which(alterL[[i]]$alterid==matched[,2])] <- net[matched[,1]]
  }
}

# again, make a matching list for the second matching matrices
# (i.e., matching egonet3 alters to prev. alters);
matchingList2 <- list()
for (i in 1:length(alterL)) { # for ego i
  matching2L <- list()
  matching2L[[1]] <- cbind(data$matching2N1.SQ001_SQ001.[i],data$matching2N1.SQ002_SQ001.[i],data$matching2N1.SQ003_SQ001.[i],data$matching2N1.SQ004_SQ001.[i],data$matching2N1.SQ005_SQ001.[i],data$matching2N1.SQ006_SQ001.[i],data$matching2N1.SQ007_SQ001.[i],data$matching2N1.SQ008_SQ001.[i],data$matching2N1.SQ009_SQ001.[i],data$matching2N1.SQ010_SQ001.[i])
  matching2L[[2]] <- rbind(
    cbind(data$matching2N2.SQ001_SQ001.[i],data$matching2N2.SQ002_SQ001.[i],data$matching2N2.SQ003_SQ001.[i],data$matching2N2.SQ004_SQ001.[i],data$matching2N2.SQ005_SQ001.[i],data$matching2N2.SQ006_SQ001.[i],data$matching2N2.SQ007_SQ001.[i],data$matching2N2.SQ008_SQ001.[i],data$matching2N2.SQ009_SQ001.[i],data$matching2N2.SQ010_SQ001.[i]),
    cbind(data$matching2N2.SQ001_SQ002.[i],data$matching2N2.SQ002_SQ002.[i],data$matching2N2.SQ003_SQ002.[i],data$matching2N2.SQ004_SQ002.[i],data$matching2N2.SQ005_SQ002.[i],data$matching2N2.SQ006_SQ002.[i],data$matching2N2.SQ007_SQ002.[i],data$matching2N2.SQ008_SQ002.[i],data$matching2N2.SQ009_SQ002.[i],data$matching2N2.SQ010_SQ002.[i]))
  matching2L[[3]] <- rbind(
    cbind(data$matching2N3.SQ001_SQ001.[i],data$matching2N3.SQ002_SQ001.[i],data$matching2N3.SQ003_SQ001.[i],data$matching2N3.SQ004_SQ001.[i],data$matching2N3.SQ005_SQ001.[i],data$matching2N3.SQ006_SQ001.[i],data$matching2N3.SQ007_SQ001.[i],data$matching2N3.SQ008_SQ001.[i],data$matching2N3.SQ009_SQ001.[i],data$matching2N3.SQ010_SQ001.[i]),
    cbind(data$matching2N3.SQ001_SQ002.[i],data$matching2N3.SQ002_SQ002.[i],data$matching2N3.SQ003_SQ002.[i],data$matching2N3.SQ004_SQ002.[i],data$matching2N3.SQ005_SQ002.[i],data$matching2N3.SQ006_SQ002.[i],data$matching2N3.SQ007_SQ002.[i],data$matching2N3.SQ008_SQ002.[i],data$matching2N3.SQ009_SQ002.[i],data$matching2N3.SQ010_SQ002.[i]),
    cbind(data$matching2N3.SQ001_SQ003.[i],data$matching2N3.SQ002_SQ003.[i],data$matching2N3.SQ003_SQ003.[i],data$matching2N3.SQ004_SQ003.[i],data$matching2N3.SQ005_SQ003.[i],data$matching2N3.SQ006_SQ003.[i],data$matching2N3.SQ007_SQ003.[i],data$matching2N3.SQ008_SQ003.[i],data$matching2N3.SQ009_SQ003.[i],data$matching2N3.SQ010_SQ003.[i]))
  matching2L[[4]] <- rbind(
    cbind(data$matching2N4.SQ001_SQ001.[i],data$matching2N4.SQ002_SQ001.[i],data$matching2N4.SQ003_SQ001.[i],data$matching2N4.SQ004_SQ001.[i],data$matching2N4.SQ005_SQ001.[i],data$matching2N4.SQ006_SQ001.[i],data$matching2N4.SQ007_SQ001.[i],data$matching2N4.SQ008_SQ001.[i],data$matching2N4.SQ009_SQ001.[i],data$matching2N4.SQ010_SQ001.[i]),
    cbind(data$matching2N4.SQ001_SQ002.[i],data$matching2N4.SQ002_SQ002.[i],data$matching2N4.SQ003_SQ002.[i],data$matching2N4.SQ004_SQ002.[i],data$matching2N4.SQ005_SQ002.[i],data$matching2N4.SQ006_SQ002.[i],data$matching2N4.SQ007_SQ002.[i],data$matching2N4.SQ008_SQ002.[i],data$matching2N4.SQ009_SQ002.[i],data$matching2N4.SQ010_SQ002.[i]),
    cbind(data$matching2N4.SQ001_SQ003.[i],data$matching2N4.SQ002_SQ003.[i],data$matching2N4.SQ003_SQ003.[i],data$matching2N4.SQ004_SQ003.[i],data$matching2N4.SQ005_SQ003.[i],data$matching2N4.SQ006_SQ003.[i],data$matching2N4.SQ007_SQ003.[i],data$matching2N4.SQ008_SQ003.[i],data$matching2N4.SQ009_SQ003.[i],data$matching2N4.SQ010_SQ003.[i]),
    cbind(data$matching2N4.SQ001_SQ004.[i],data$matching2N4.SQ002_SQ004.[i],data$matching2N4.SQ003_SQ004.[i],data$matching2N4.SQ004_SQ004.[i],data$matching2N4.SQ005_SQ004.[i],data$matching2N4.SQ006_SQ004.[i],data$matching2N4.SQ007_SQ004.[i],data$matching2N4.SQ008_SQ004.[i],data$matching2N4.SQ009_SQ004.[i],data$matching2N4.SQ010_SQ004.[i]))
  matching2L[[5]] <- rbind(
    cbind(data$matching2N5.SQ001_SQ001.[i],data$matching2N5.SQ002_SQ001.[i],data$matching2N5.SQ003_SQ001.[i],data$matching2N5.SQ004_SQ001.[i],data$matching2N5.SQ005_SQ001.[i],data$matching2N5.SQ006_SQ001.[i],data$matching2N5.SQ007_SQ001.[i],data$matching2N5.SQ008_SQ001.[i],data$matching2N5.SQ009_SQ001.[i],data$matching2N5.SQ010_SQ001.[i]),
    cbind(data$matching2N5.SQ001_SQ002.[i],data$matching2N5.SQ002_SQ002.[i],data$matching2N5.SQ003_SQ002.[i],data$matching2N5.SQ004_SQ002.[i],data$matching2N5.SQ005_SQ002.[i],data$matching2N5.SQ006_SQ002.[i],data$matching2N5.SQ007_SQ002.[i],data$matching2N5.SQ008_SQ002.[i],data$matching2N5.SQ009_SQ002.[i],data$matching2N5.SQ010_SQ002.[i]),
    cbind(data$matching2N5.SQ001_SQ003.[i],data$matching2N5.SQ002_SQ003.[i],data$matching2N5.SQ003_SQ003.[i],data$matching2N5.SQ004_SQ003.[i],data$matching2N5.SQ005_SQ003.[i],data$matching2N5.SQ006_SQ003.[i],data$matching2N5.SQ007_SQ003.[i],data$matching2N5.SQ008_SQ003.[i],data$matching2N5.SQ009_SQ003.[i],data$matching2N5.SQ010_SQ003.[i]),
    cbind(data$matching2N5.SQ001_SQ004.[i],data$matching2N5.SQ002_SQ004.[i],data$matching2N5.SQ003_SQ004.[i],data$matching2N5.SQ004_SQ004.[i],data$matching2N5.SQ005_SQ004.[i],data$matching2N5.SQ006_SQ004.[i],data$matching2N5.SQ007_SQ004.[i],data$matching2N5.SQ008_SQ004.[i],data$matching2N5.SQ009_SQ004.[i],data$matching2N5.SQ010_SQ004.[i]),
    cbind(data$matching2N5.SQ001_SQ005.[i],data$matching2N5.SQ002_SQ005.[i],data$matching2N5.SQ003_SQ005.[i],data$matching2N5.SQ004_SQ005.[i],data$matching2N5.SQ005_SQ005.[i],data$matching2N5.SQ006_SQ005.[i],data$matching2N5.SQ007_SQ005.[i],data$matching2N5.SQ008_SQ005.[i],data$matching2N5.SQ009_SQ005.[i],data$matching2N5.SQ010_SQ005.[i]))
  matchingList2[[i]] <- matching2L
}

for (i in 1:length(matchingList2)) {    # for ego i
  mL <- matchingList2[[i]]              # get the matching list 2
  ns <- ns3[[i]]                        # get the size of egonet3
  if(ns>0) {                            # if ns=0, no matching was done!
    mm <- as.matrix(mL[[ns]])           # and the corresponding matrix
    matched <- which(mm==1, arr.ind=T)  # retrieve array indices
    net <- net3[i,]
    alterL[[i]]$name3[matched[,2]] <- net[matched[,1]]
  }
}

# same for matching 3 (i.e., egonet4 with egonets 1-3)
matchingList3 <- list()
for (i in 1:length(alterL)) { # for ego i
  matching3L <- list()
  matching3L[[1]] <- cbind(data$matching3N1.SQ001_SQ001.[i],data$matching3N1.SQ002_SQ001.[i],data$matching3N1.SQ003_SQ001.[i],data$matching3N1.SQ004_SQ001.[i],data$matching3N1.SQ005_SQ001.[i],data$matching3N1.SQ006_SQ001.[i],data$matching3N1.SQ007_SQ001.[i],data$matching3N1.SQ008_SQ001.[i],data$matching3N1.SQ009_SQ001.[i],data$matching3N1.SQ010_SQ001.[i], data$matching3N1.SQ011_SQ001.[i], data$matching3N1.SQ012_SQ001.[i], data$matching3N1.SQ013_SQ001.[i], data$matching3N1.SQ014_SQ001.[i], data$matching3N1.SQ015_SQ001.[i])
  matching3L[[2]] <- rbind(
    cbind(data$matching3N2.SQ001_SQ001.[i],data$matching3N2.SQ002_SQ001.[i],data$matching3N2.SQ003_SQ001.[i],data$matching3N2.SQ004_SQ001.[i],data$matching3N2.SQ005_SQ001.[i],data$matching3N2.SQ006_SQ001.[i],data$matching3N2.SQ007_SQ001.[i],data$matching3N2.SQ008_SQ001.[i],data$matching3N2.SQ009_SQ001.[i],data$matching3N2.SQ010_SQ001.[i], data$matching3N2.SQ011_SQ001.[i], data$matching3N2.SQ012_SQ001.[i], data$matching3N2.SQ013_SQ001.[i], data$matching3N2.SQ014_SQ001.[i], data$matching3N2.SQ015_SQ001.[i]),
    cbind(data$matching3N2.SQ001_SQ002.[i],data$matching3N2.SQ002_SQ002.[i],data$matching3N2.SQ003_SQ002.[i],data$matching3N2.SQ004_SQ002.[i],data$matching3N2.SQ005_SQ002.[i],data$matching3N2.SQ006_SQ002.[i],data$matching3N2.SQ007_SQ002.[i],data$matching3N2.SQ008_SQ002.[i],data$matching3N2.SQ009_SQ002.[i],data$matching3N2.SQ010_SQ002.[i], data$matching3N2.SQ011_SQ002.[i], data$matching3N2.SQ012_SQ002.[i], data$matching3N2.SQ013_SQ002.[i], data$matching3N2.SQ014_SQ002.[i], data$matching3N2.SQ015_SQ002.[i]))
  matching3L[[3]] <- rbind(
    cbind(data$matching3N3.SQ001_SQ001.[i],data$matching3N3.SQ002_SQ001.[i],data$matching3N3.SQ003_SQ001.[i],data$matching3N3.SQ004_SQ001.[i],data$matching3N3.SQ005_SQ001.[i],data$matching3N3.SQ006_SQ001.[i],data$matching3N3.SQ007_SQ001.[i],data$matching3N3.SQ008_SQ001.[i],data$matching3N3.SQ009_SQ001.[i],data$matching3N3.SQ010_SQ001.[i], data$matching3N3.SQ011_SQ001.[i], data$matching3N3.SQ012_SQ001.[i], data$matching3N3.SQ013_SQ001.[i], data$matching3N3.SQ014_SQ001.[i], data$matching3N3.SQ015_SQ001.[i]),
    cbind(data$matching3N3.SQ001_SQ002.[i],data$matching3N3.SQ002_SQ002.[i],data$matching3N3.SQ003_SQ002.[i],data$matching3N3.SQ004_SQ002.[i],data$matching3N3.SQ005_SQ002.[i],data$matching3N3.SQ006_SQ002.[i],data$matching3N3.SQ007_SQ002.[i],data$matching3N3.SQ008_SQ002.[i],data$matching3N3.SQ009_SQ002.[i],data$matching3N3.SQ010_SQ002.[i], data$matching3N3.SQ011_SQ002.[i], data$matching3N3.SQ012_SQ002.[i], data$matching3N3.SQ013_SQ002.[i], data$matching3N3.SQ014_SQ002.[i], data$matching3N3.SQ015_SQ002.[i]),
    cbind(data$matching3N3.SQ001_SQ003.[i],data$matching3N3.SQ002_SQ003.[i],data$matching3N3.SQ003_SQ003.[i],data$matching3N3.SQ004_SQ003.[i],data$matching3N3.SQ005_SQ003.[i],data$matching3N3.SQ006_SQ003.[i],data$matching3N3.SQ007_SQ003.[i],data$matching3N3.SQ008_SQ003.[i],data$matching3N3.SQ009_SQ003.[i],data$matching3N3.SQ010_SQ003.[i], data$matching3N3.SQ011_SQ003.[i], data$matching3N3.SQ012_SQ003.[i], data$matching3N3.SQ013_SQ003.[i], data$matching3N3.SQ014_SQ003.[i], data$matching3N3.SQ015_SQ003.[i]))
  matching3L[[4]] <- rbind(
    cbind(data$matching3N4.SQ001_SQ001.[i],data$matching3N4.SQ002_SQ001.[i],data$matching3N4.SQ003_SQ001.[i],data$matching3N4.SQ004_SQ001.[i],data$matching3N4.SQ005_SQ001.[i],data$matching3N4.SQ006_SQ001.[i],data$matching3N4.SQ007_SQ001.[i],data$matching3N4.SQ008_SQ001.[i],data$matching3N4.SQ009_SQ001.[i],data$matching3N4.SQ010_SQ001.[i], data$matching3N4.SQ011_SQ001.[i], data$matching3N4.SQ012_SQ001.[i], data$matching3N4.SQ013_SQ001.[i], data$matching3N4.SQ014_SQ001.[i], data$matching3N4.SQ015_SQ001.[i]),
    cbind(data$matching3N4.SQ001_SQ002.[i],data$matching3N4.SQ002_SQ002.[i],data$matching3N4.SQ003_SQ002.[i],data$matching3N4.SQ004_SQ002.[i],data$matching3N4.SQ005_SQ002.[i],data$matching3N4.SQ006_SQ002.[i],data$matching3N4.SQ007_SQ002.[i],data$matching3N4.SQ008_SQ002.[i],data$matching3N4.SQ009_SQ002.[i],data$matching3N4.SQ010_SQ002.[i], data$matching3N4.SQ011_SQ002.[i], data$matching3N4.SQ012_SQ002.[i], data$matching3N4.SQ013_SQ002.[i], data$matching3N4.SQ014_SQ002.[i], data$matching3N4.SQ015_SQ002.[i]),
    cbind(data$matching3N4.SQ001_SQ003.[i],data$matching3N4.SQ002_SQ003.[i],data$matching3N4.SQ003_SQ003.[i],data$matching3N4.SQ004_SQ003.[i],data$matching3N4.SQ005_SQ003.[i],data$matching3N4.SQ006_SQ003.[i],data$matching3N4.SQ007_SQ003.[i],data$matching3N4.SQ008_SQ003.[i],data$matching3N4.SQ009_SQ003.[i],data$matching3N4.SQ010_SQ003.[i], data$matching3N4.SQ011_SQ003.[i], data$matching3N4.SQ012_SQ003.[i], data$matching3N4.SQ013_SQ003.[i], data$matching3N4.SQ014_SQ003.[i], data$matching3N4.SQ015_SQ003.[i]),
    cbind(data$matching3N4.SQ001_SQ003.[i],data$matching3N4.SQ002_SQ003.[i],data$matching3N4.SQ003_SQ003.[i],data$matching3N4.SQ004_SQ003.[i],data$matching3N4.SQ005_SQ003.[i],data$matching3N4.SQ006_SQ003.[i],data$matching3N4.SQ007_SQ003.[i],data$matching3N4.SQ008_SQ003.[i],data$matching3N4.SQ009_SQ003.[i],data$matching3N4.SQ010_SQ003.[i], data$matching3N4.SQ011_SQ003.[i], data$matching3N4.SQ012_SQ003.[i], data$matching3N4.SQ013_SQ003.[i], data$matching3N4.SQ014_SQ003.[i], data$matching3N4.SQ015_SQ003.[i]),
    cbind(data$matching3N4.SQ001_SQ004.[i],data$matching3N4.SQ002_SQ004.[i],data$matching3N4.SQ003_SQ004.[i],data$matching3N4.SQ004_SQ004.[i],data$matching3N4.SQ005_SQ004.[i],data$matching3N4.SQ006_SQ004.[i],data$matching3N4.SQ007_SQ004.[i],data$matching3N4.SQ008_SQ004.[i],data$matching3N4.SQ009_SQ004.[i],data$matching3N4.SQ010_SQ004.[i], data$matching3N4.SQ011_SQ004.[i], data$matching3N4.SQ012_SQ004.[i], data$matching3N4.SQ013_SQ004.[i], data$matching3N4.SQ014_SQ004.[i], data$matching3N4.SQ015_SQ004.[i]))
  matching3L[[5]] <- rbind(
    cbind(data$matching3N5.SQ001_SQ001.[i],data$matching3N5.SQ002_SQ001.[i],data$matching3N5.SQ003_SQ001.[i],data$matching3N5.SQ004_SQ001.[i],data$matching3N5.SQ005_SQ001.[i],data$matching3N5.SQ006_SQ001.[i],data$matching3N5.SQ007_SQ001.[i],data$matching3N5.SQ008_SQ001.[i],data$matching3N5.SQ009_SQ001.[i],data$matching3N5.SQ010_SQ001.[i], data$matching3N5.SQ011_SQ001.[i], data$matching3N5.SQ012_SQ001.[i], data$matching3N5.SQ013_SQ001.[i], data$matching3N5.SQ014_SQ001.[i], data$matching3N5.SQ015_SQ001.[i]),
    cbind(data$matching3N5.SQ001_SQ002.[i],data$matching3N5.SQ002_SQ002.[i],data$matching3N5.SQ003_SQ002.[i],data$matching3N5.SQ004_SQ002.[i],data$matching3N5.SQ005_SQ002.[i],data$matching3N5.SQ006_SQ002.[i],data$matching3N5.SQ007_SQ002.[i],data$matching3N5.SQ008_SQ002.[i],data$matching3N5.SQ009_SQ002.[i],data$matching3N5.SQ010_SQ002.[i], data$matching3N5.SQ011_SQ002.[i], data$matching3N5.SQ012_SQ002.[i], data$matching3N5.SQ013_SQ002.[i], data$matching3N5.SQ014_SQ002.[i], data$matching3N5.SQ015_SQ002.[i]),
    cbind(data$matching3N5.SQ001_SQ003.[i],data$matching3N5.SQ002_SQ003.[i],data$matching3N5.SQ003_SQ003.[i],data$matching3N5.SQ004_SQ003.[i],data$matching3N5.SQ005_SQ003.[i],data$matching3N5.SQ006_SQ003.[i],data$matching3N5.SQ007_SQ003.[i],data$matching3N5.SQ008_SQ003.[i],data$matching3N5.SQ009_SQ003.[i],data$matching3N5.SQ010_SQ003.[i], data$matching3N5.SQ011_SQ003.[i], data$matching3N5.SQ012_SQ003.[i], data$matching3N5.SQ013_SQ003.[i], data$matching3N5.SQ014_SQ003.[i], data$matching3N5.SQ015_SQ003.[i]),
    cbind(data$matching3N5.SQ001_SQ003.[i],data$matching3N5.SQ002_SQ003.[i],data$matching3N5.SQ003_SQ003.[i],data$matching3N5.SQ004_SQ003.[i],data$matching3N5.SQ005_SQ003.[i],data$matching3N5.SQ006_SQ003.[i],data$matching3N5.SQ007_SQ003.[i],data$matching3N5.SQ008_SQ003.[i],data$matching3N5.SQ009_SQ003.[i],data$matching3N5.SQ010_SQ003.[i], data$matching3N5.SQ011_SQ003.[i], data$matching3N5.SQ012_SQ003.[i], data$matching3N5.SQ013_SQ003.[i], data$matching3N5.SQ014_SQ003.[i], data$matching3N5.SQ015_SQ003.[i]),
    cbind(data$matching3N5.SQ001_SQ005.[i],data$matching3N5.SQ002_SQ005.[i],data$matching3N5.SQ003_SQ005.[i],data$matching3N5.SQ004_SQ005.[i],data$matching3N5.SQ005_SQ005.[i],data$matching3N5.SQ006_SQ005.[i],data$matching3N5.SQ007_SQ005.[i],data$matching3N5.SQ008_SQ005.[i],data$matching3N5.SQ009_SQ005.[i],data$matching3N5.SQ010_SQ005.[i], data$matching3N5.SQ011_SQ005.[i], data$matching3N5.SQ012_SQ005.[i], data$matching3N5.SQ013_SQ005.[i], data$matching3N5.SQ014_SQ005.[i], data$matching3N5.SQ015_SQ005.[i]))
  matchingList3[[i]] <- matching3L
}

for (i in 1:length(matchingList3)) {    # for ego i
  mL <- matchingList3[[i]]              # get the matching list 2
  ns <- ns4[[i]]                        # get the size of egonet4
  if(ns>0) {                            # if ns=0, no matching was done!
    mm <- as.matrix(mL[[ns]])           # and the corresponding matrix
    matched <- which(mm==1, arr.ind=T)  # retrieve array indices
    net <- net4[i,]
    alterL[[i]]$name4[matched[,2]] <- net[matched[,1]]
  }
}

# i use the name interpreter data to add alter characteristics
# i make a data-frame of alters' gender
# in the survey, in name-interpreter questions, only unique (i.e., non-matched)
# alters were listed...
# thus, alter ids without a gender assigned to them are non-uniques, and can
# later be filtered out.

df_gender <- data.frame(
  p1 = data$gender.SQ001.,
  p2 = data$gender.SQ002.,
  p3 = data$gender.SQ003.,
  p4 = data$gender.SQ004.,
  p5 = data$gender.SQ005.,
  p6 = data$gender.SQ006.,
  p7 = data$gender.SQ007.,
  p8 = data$gender.SQ008.,
  p9 = data$gender.SQ009.,
  p10= data$gender.SQ010.,
  p11= data$gender.SQ011.,
  p12= data$gender.SQ012.,
  p13= data$gender.SQ013.,
  p14= data$gender.SQ014.,
  p15= data$gender.SQ015.,
  p16= data$gender.SQ016.,
  p17= data$gender.SQ017.,
  p18= data$gender.SQ018.,
  p19= data$gender.SQ019.,
  p20= data$gender.SQ020.)

for (i in 1:length(alterL)) {
  alterL[[i]]$alter_gender <- 
    ifelse(unlist(df_gender[i,], use.names=F)=="Man", 0,  # male = ref.
           ifelse(unlist(df_gender[i,], use.names=F)=="Vrouw", 1,
                  ifelse(unlist(df_gender[i,], use.names=F)=="Anders", 2, "")))
}

# same for age...
df_age <- data.frame(
  p1 = data$age.SQ001.,
  p2 = data$age.SQ002.,
  p3 = data$age.SQ003.,
  p4 = data$age.SQ004.,
  p5 = data$age.SQ005.,
  p6 = data$age.SQ006.,
  p7 = data$age.SQ007.,
  p8 = data$age.SQ008.,
  p9 = data$age.SQ009.,
  p10= data$age.SQ010.,
  p11= data$age.SQ011.,
  p12= data$age.SQ012.,
  p13= data$age.SQ013.,
  p14= data$age.SQ014.,
  p15= data$age.SQ015.,
  p16= data$age.SQ016.,
  p17= data$age.SQ017.,
  p18= data$age.SQ018.,
  p19= data$age.SQ019.,
  p20= data$age.SQ020.)

for (i in 1:length(alterL)) {
  alterL[[i]]$alter_age <- 
    ifelse(unlist(df_age[i,], use.names=F)=="Jonger dan 18 jaar", 16, #???
           ifelse(unlist(df_age[i,], use.names=F)=="18 tot 21 jaar", 20,
                  ifelse(unlist(df_age[i,], use.names=F)=="22 tot 25 jaar", 23,
                         ifelse(unlist(df_age[i,], use.names=F)=="26 tot 30 jaar", 28,
                                ifelse(unlist(df_age[i,], use.names=F)=="31 tot 40 jaar", 35,
                                       ifelse(unlist(df_age[i,], use.names=F)=="Ouder dan 40 jaar", 45, #???
                                              ifelse(unlist(df_age[i,], use.names=F)=="Weet ik niet", NA, # i don't know = missing
                                                     unlist(df_age[i,], use.names=F))))))))}

# education... was asked in w2. for all alters (thus in w2, and unique names of w1)
# but w1 names were only listed if they did not correspond to w2 alters...
# ...

# political placement of alters on left-right spectrum (as perceived by ego)
df_pol <- data.frame(
  p1 = data$P5.SQ001.,
  p2 = data$P5.SQ002.,
  p3 = data$P5.SQ003.,
  p4 = data$P5.SQ004.,
  p5 = data$P5.SQ005.,
  p6 = data$P5.SQ006.,
  p7 = data$P5.SQ007.,
  p8 = data$P5.SQ008.,
  p9 = data$P5.SQ009.,
  p10= data$P5.SQ010.,
  p11= data$P5.SQ011.,
  p12= data$P5.SQ012.,
  p13= data$P5.SQ013.,
  p14= data$P5.SQ014.,
  p15= data$P5.SQ015.,
  p16= data$P5.SQ016.,
  p17= data$P5.SQ017.,
  p18= data$P5.SQ018.,
  p19= data$P5.SQ019.,
  p20= data$P5.SQ020.)


for (i in 1:length(alterL)) {
  alter_placement <- unlist(df_pol[i,],use.names=F)
  # extract numbers from strings
  alter_placement <- stringr::str_extract(alter_placement,  pattern = "\\(?[0-9,.]+\\)?")
  alterL[[i]]$alter_pol <- alter_placement
}

# before we can construct similarity indices, we must add ego-attributes
for (i in 1:length(alterL)) {
  #  gender
  alterL[[i]]$ego_gender <- ifelse(data$A1[i] == "Man", 0,
                                   ifelse(data$A1[i] == "Vrouw", 1,
                                          ifelse(data$A1[i] == "Overige", 2,
                                                 NA)))
  # education 
  # @RF: these score should correspond to scores given to alter educ...
  alterL[[i]]$ego_educ <- ifelse(data$T1[i] == "aan de Hogeschool van Arnhem en Nijmegen (HAN)", "hbo", "universiteit" )
  
  # age
  # calculated as the difference between submission date and birthdate
  # in years.
  birth_date <- as.Date(data$A2)
  x_date <- as.Date(data$submitdate)
  require(lubridate)
  alterL[[i]]$ego_age <- trunc((birth_date[i] %--% x_date[i]) / years(1))
  
  # political orientation (left-right)
  ego_placement <- stringr::str_extract(data$P1.SQ001.,  pattern = "\\(?[0-9,.]+\\)?")
  alterL[[i]]$ego_pol <- as.numeric(ego_placement[i])
}

# i filter out the unique, non-duplicate alters;
# by excluding alters with empty strings for gender attribute
for ( i in 1:length(alterL)) {
  alterL[[i]] <- alterL[[i]][which(alterL[[i]]$alter_gender!=""),]
  # and replace the alter id: 1 : no. unique alters
  alterL[[i]]$alterid <- 1:nrow(alterL[[i]])
}

# dyadic similarity:
for (i in 1:length(alterL))  { # for ego i
  # get attributes of ego
  agei <- alterL[[i]]$ego_age[1]
  genderi <- alterL[[i]]$ego_gender[1]
  #educi <- alterL[[i]]$ego_educ[1]
  poli <- alterL[[i]]$ego_pol[1]
  
  for (j in 1:max(alterL[[i]]$alterid)) { # for alter j
    # calculate "same gender" (0/1)
    genderj <- as.numeric(alterL[[i]]$alter_gender[j]) # get alter j gender
    same <- ifelse(genderi==genderj, 1, 0)
    alterL[[i]]$same_gender[which(alterL[[i]]$alterid==j)] <- same
    
    # calculate similarity for age and political orientation
    # @RF.. to-do: education
    
    # @RF... i may want to construct similarity indices for continues variables
    # sim^z_ij = 1 - |z_i - z_j| / rang_z
    # this is beneficial, as index values range between 0 and 1...
    # here, some conditions are relevant; as similarity would be -INF is rang_z=0;
    # and incalculable if z_j = NA (unknown) [and/or z_i = NA (i.e., for political orientation)]
    
    # for now... i calculate similarity/homophily as the absolute difference between
    # alter and ego value (cf. Marin & Hampton 2019); "easy method"
    agej <- as.numeric(alterL[[i]]$alter_age[j]) # get alter j age
    difage <- abs(agei - agej) # difference score
    # so higher values represent *less* similarity
    if( !is.na (agej) ) { # similarity only calculable if z_j is known!
      alterL[[i]]$dif_age[which(alterL[[i]]$alterid==j)] <- difage
    } else { alterL[[i]]$dif_age[which(alterL[[i]]$alterid==j)] <- NA}
  }
  
  # dyadic similarity:
  for (i in 1:length(alterL))  { # for ego i
    # get attributes of ego
    agei <- alterL[[i]]$ego_age[1]
    genderi <- alterL[[i]]$ego_gender[1]
    #educi <- alterL[[i]]$ego_educ[1]
    poli <- alterL[[i]]$ego_pol[1]
    
    for (j in 1:max(alterL[[i]]$alterid)) { # for alter j
      # calculate "same gender" (0/1)
      genderj <- as.numeric(alterL[[i]]$alter_gender[j]) # get alter j gender
      same <- ifelse(genderi==genderj, 1, 0)
      alterL[[i]]$same_gender[which(alterL[[i]]$alterid==j)] <- same
      
      # calculate similarity for age and political orientation
      # @RF.. to-do: education
      
      # @RF... i may want to construct similarity indices for continues variables
      # sim^z_ij = 1 - |z_i - z_j| / rang_z
      # probably for political orientation, as the range (scale) is known...
      # this is beneficial, as index values range between 0 and 1...
      # here, some conditions are relevant; as similarity would be -INF is rang_z=0;
      # and incalculable if z_j and/or z_i = NA (unknown)
      
      # for now... i calculate similarity/homophily as the absolute difference between
      # alter and ego value (cf. Marin & Hampton 2019);
      agej <- as.numeric(alterL[[i]]$alter_age[j]) # get alter j attributes
      polj <- as.numeric(alterL[[i]]$alter_pol[j])
      
      difage <- abs(agei - agej) # difference scores
      difpol <- abs(poli - polj)
      # higher values represent less similarity
      
      if( !is.na (agej) ) { # age similarity only calculable if z_j is known!
        alterL[[i]]$dif_age[which(alterL[[i]]$alterid==j)] <- difage
      } else { alterL[[i]]$dif_age[which(alterL[[i]]$alterid==j)] <- NA}
      
      if( !is.na (polj) & !is.na(poli) ) { # pol. similarity only if zi AND zj are known
        alterL[[i]]$dif_pol[which(alterL[[i]]$alterid==j)] <- difpol
      } else { alterL[[i]]$dif_pol[which(alterL[[i]]$alterid==j)] <- NA}
    }
    
  }
}

# based on list of data-frames for each ego, i make a long data-frame with 
# alters nested in egos
# nrow per ego depends on netsize
ns <- vector()
for (i in 1:length(alterL)){
  ns[i] <- nrow(alterL[[i]])
}

df <- data.frame(
  ego = rep(1:length(alterL),ns)
)

# add ego-level variables
df$ego_gender <- NA
df$ego_age <- NA
df$ego_educ <- NA
df$ego_pol <- NA
#...
#

for (i in unique(df$ego)) { # for ego
  df$ego_gender[which(df$ego==i)] <- alterL[[i]]$ego_gender[1]
  df$ego_age[which(df$ego==i)] <- alterL[[i]]$ego_age[1]
  df$ego_educ[which(df$ego==i)] <- alterL[[i]]$ego_educ[1]
  df$ego_pol[which(df$ego==i)] <- alterL[[i]]$ego_pol[1]
  #@RF: perhaps add missing dummy for political orienation... interesting category?
}

# make alter ids per ego
df$alter <- NA
for (i in unique(df$ego)) {
  df$alter[which(df$ego==i)] <- 1:nrow(df[which(df$ego==i),])
}

# binary attributes, indicating whether alters appeared in each of the egonets
df$cdn <- NA
df$study <- NA
df$bff <- NA
df$csn <- NA

for (i in unique(df$ego)) {  
  for (j in 1:nrow(df[which(df$ego==i),])) { # for alters nested in ego
    # find out if names denoting alter j appear in the 4 egonets
    alter <- unlist(alterL[[i]][j,6:9], use.names = F) # get names alter j
    alter <- alter[!is.na(alter)] # exclude NAs
    cdn <- alter %in% net1[i,]
    study <- alter %in% net2[i,]
    bff <- alter %in% net3[i,]
    csn <- alter %in% net4[i,]
    # and if so, give alter j score 1 on indicators; 0 otherwise
    df$cdn[which(df$ego==i & df$alter==j)] <- ifelse("TRUE" %in% cdn, 1, 0)
    df$study[which(df$ego==i & df$alter==j)] <- ifelse("TRUE" %in% study, 1, 0)
    df$bff[which(df$ego==i & df$alter==j)] <- ifelse("TRUE" %in% bff, 1, 0)
    df$csn[which(df$ego==i & df$alter==j)] <- ifelse("TRUE" %in% csn, 1, 0)
  }
}

# add alter level attributes
df$alter_gender <- NA
df$alter_age <- NA
df$alter_educ <- NA
df$alter_pol <- NA
#...

for (i in unique(df$ego)) { # for ego
  for (j in unique(df$alter[which(df$ego==i)])) { # for alter
    df$alter_gender[which(df$ego==i & df$alter==j)] <- alterL[[i]]$alter_gender[j]
    df$alter_age[which(df$ego==i & df$alter==j)] <- alterL[[i]]$alter_age[j]
    df$alter_educ[which(df$ego==i & df$alter==j)] <- alterL[[i]]$alter_educ[j]
    df$alter_pol[which(df$ego==i & df$alter==j)] <- alterL[[i]]$alter_pol[j]
  }
}

# dyadic level
df$same_gender = NA
df$sim_educ = NA
df$dif_age = NA
df$dif_pol = NA

for (i in unique(df$ego)) { # for ego
  for (j in unique(df$alter[which(df$ego==i)])) { # for alter
    df$same_gender[which(df$ego==i & df$alter==j)] <- alterL[[i]]$same_gender[j]
    df$sim_educ[which(df$ego==i & df$alter==j)] <- alterL[[i]]$sim_educ[j]
    df$dif_age[which(df$ego==i & df$alter==j)] <- alterL[[i]]$dif_age[j]
    df$dif_pol[which(df$ego==i & df$alter==j)] <- alterL[[i]]$dif_pol[j]    
  }
}

# as a last step, i have to find out whether alters were maintained in w2
df$survive <- NA
# In wave 2, another matching procedure was used;
# in rows, alters named in w2 are listed; columns denote (unique) alters of w1,
# so the same one as our data-frame.
# again, i made multiple matrices, conditional on the no. of unique alters of w1
# (15, to be precise)
# if, in one of these matrices, column j was marked as corresponding to a
# named alter in w2, then alter j did, indeed, survive...

# subset w1-w2 matching matrices; and email
w2 <- data2[,c(637:936, 1427)]
# add a id variable to the original data, and subset this with the email
data$id <- 1:nrow(data)
#tail(names(data))
#length(data)
d <- data[,c(1029:1030)]
# merge the data-set with the w1-w2 matching matrices
d <- merge(w2, d, by="email")
# sort by the id variable, so that the ordening of responses is the same as our
# long dataframe
d <- data.frame(d[order(d$id, decreasing = F), ])
# and reorder rownames
rownames(d) <- 1:length(rownames(d))

for (i in 1:nrow(d)) {  # for ego i
  
  matchingL <- list()  # make a list of matching matrices
  {
    matchingL[[1]] <- d[i,2:21]
    matchingL[[2]] <- d[i,22:41]
    matchingL[[3]] <- d[i,42:61]
    matchingL[[4]] <- d[i,62:81]
    matchingL[[5]] <- d[i,82:101]
    matchingL[[6]] <- d[i,102:121]
    matchingL[[7]] <- d[i,122:141]
    matchingL[[8]] <- d[i,142:161]
    matchingL[[9]] <- d[i,162:181]
    matchingL[[10]] <- d[i,182:201]
    matchingL[[11]] <- d[i,202:221]
    matchingL[[12]] <- d[i,222:241]
    matchingL[[13]] <- d[i,242:261]
    matchingL[[14]] <- d[i,262:281]
    matchingL[[15]] <- d[i,282:301]
  }
  # get netsize of ego i
  ns <- max(df$alter[which(df$ego==i)])
  # get the corresponding matrix
  mm <- matchingL[[ns]]
  # unlist the answers given
  ans <- unlist(mm, use.names = F)
  # use 'stringr' to extract numbers in these answers,
  # they refer to the id of "survived" alters
  id <- unlist(stringr::str_extract_all(ans,"\\(?[0-9,.]+\\)?"))
  id <- id[!is.na(id)] # exclude NA
  # if alter id of ego i corresponds to this id, they did indeed survive:
  
  df$survive[which(df$ego==i)] <- ifelse(df$alter[which(df$ego==i)] %in% id, 1, 0)
  
}

##################################################################################

# add other variables.....
# education
# alter educ was asked in w2.
# merge the data.
d <- merge(data, data2, by="email")
# sort
d <- data.frame(d[order(d$id, decreasing = F), ])

# i asked the education level of all alters, of w1 and w2.
# i only named w2 alters that were unmatched and new compared to w1.
# all (unique) w1-alters were listed.
# d$q0r117.SQ021. - d$q0r117.SQ035. 

for (i in unique(df$ego)) { # for ego i  
  # subset alter education
  educj <- cbind(d$q0r117.SQ021.[i],d$q0r117.SQ022.[i],d$q0r117.SQ023.[i],d$q0r117.SQ024.[i],d$q0r117.SQ025.[i],d$q0r117.SQ026.[i],d$q0r117.SQ027.[i],d$q0r117.SQ028.[i],
                 d$q0r117.SQ029.[i],d$q0r117.SQ030.[i],d$q0r117.SQ031.[i],d$q0r117.SQ032.[i],d$q0r117.SQ033.[i],d$q0r117.SQ034.[i],d$q0r117.SQ035.[i])
  for (j in unique(df$alter[which(df$ego==i)])) { # for alter j
    # assign education level
    df$alter_educ[which(df$ego==i & df$alter==j)] <- educj[j]
  }
}

# @RF; for now use 5 categories; later on, operationalize education in years;
prim <- c("lagere school", "vmbo, mavo")
lowsec <- c("mbo")
highsec <- c( "havo", "vwo / gymnasium")
lowtert <- "hbo"
hightert <- "universiteit"

for (i in unique(df$ego)) {
  for (j in unique(df$alter[which(df$ego==i)])) {
    
    df$alter_educ[which(df$ego==i & df$alter==j)] <-
      ifelse(    
        df$alter_educ[which(df$ego==i & df$alter==j)] %in% prim, 1,
        ifelse(df$alter_educ[which(df$ego==i & df$alter==j)] %in% lowsec, 2,
               ifelse(df$alter_educ[which(df$ego==i & df$alter==j)] %in% highsec, 3,
                      ifelse( df$alter_educ[which(df$ego==i & df$alter==j)] %in% lowtert, 4, 
                              ifelse(  df$alter_educ[which(df$ego==i & df$alter==j)] %in% hightert, 5,
                                       NA)))))
  }
}
df$alter_educ <- as.numeric(df$alter_educ)
# ego educ
df$ego_educ <- ifelse(df$ego_educ=="hbo", 4, 5)

# @RF. educ in years similarity could be defined as absolute difference
# since i am now dealing with categories, i use a "same" measure to measure educational similarity.
df$sim_educ <- ifelse(df$ego_educ==df$alter_educ, 1, 0) # do not know (missing), here treated as dissimilar

# and add tie strength, duration, physical proximity
df$duration <- NA
df$proximity <- NA
df$frequency <- NA
df$closeness <- NA

for (i in unique(df$ego)) {
  dur <- cbind(data$duur.SQ001.[i], data$duur.SQ002.[i], data$duur.SQ003.[i], data$duur.SQ004.[i], data$duur.SQ005.[i],
               data$duur.SQ006.[i], data$duur.SQ007.[i], data$duur.SQ008.[i], data$duur.SQ009.[i], data$duur.SQ010.[i],
               data$duur.SQ011.[i], data$duur.SQ012.[i], data$duur.SQ013.[i], data$duur.SQ014.[i], data$duur.SQ015.[i],
               data$duur.SQ016.[i], data$duur.SQ017.[i], data$duur.SQ018.[i], data$duur.SQ019.[i], data$duur.SQ020.[i])
  dur <- dur[!dur==""]
  
  prox <- cbind(data$prox.SQ001.[i], data$prox.SQ002.[i], data$prox.SQ003.[i], data$prox.SQ004.[i], data$prox.SQ005.[i],
                data$prox.SQ006.[i], data$prox.SQ007.[i], data$prox.SQ008.[i], data$prox.SQ009.[i], data$prox.SQ010.[i],
                data$prox.SQ011.[i], data$prox.SQ012.[i], data$prox.SQ013.[i], data$prox.SQ014.[i], data$prox.SQ015.[i],
                data$prox.SQ016.[i], data$prox.SQ017.[i], data$prox.SQ018.[i], data$prox.SQ019.[i], data$prox.SQ020.[i])
  prox <- prox[!prox==""]
  
  freq <- cbind(data$freq.SQ001.[i], data$freq.SQ002.[i], data$freq.SQ003.[i], data$freq.SQ004.[i], data$freq.SQ005.[i],
                data$freq.SQ006.[i], data$freq.SQ007.[i], data$freq.SQ008.[i], data$freq.SQ009.[i], data$freq.SQ010.[i],
                data$freq.SQ011.[i], data$freq.SQ012.[i], data$freq.SQ013.[i], data$freq.SQ014.[i], data$freq.SQ015.[i],
                data$freq.SQ016.[i], data$freq.SQ017.[i], data$freq.SQ018.[i], data$freq.SQ019.[i], data$freq.SQ020.[i])
  freq <- freq[!freq==""]
  
  close <- cbind(data$close.SQ001.[i], data$close.SQ002.[i], data$close.SQ003.[i], data$close.SQ004.[i], data$close.SQ005.[i],
                 data$close.SQ006.[i], data$close.SQ007.[i], data$close.SQ008.[i], data$close.SQ009.[i], data$close.SQ010.[i],
                 data$close.SQ011.[i], data$close.SQ012.[i], data$close.SQ013.[i], data$close.SQ014.[i], data$close.SQ015.[i],
                 data$close.SQ016.[i], data$close.SQ017.[i], data$close.SQ018.[i], data$close.SQ019.[i], data$close.SQ020.[i])
  close <- close[!close==""]
  

  for (j in unique(df$alter[which(df$ego==i)])) {
    df$duration[which(df$ego==i & df$alter==j)] <- dur[j]
    df$proximity[which(df$ego==i & df$alter==j)] <- prox[j]
    df$frequency[which(df$ego==i & df$alter==j)] <- freq[j]
    df$closeness[which(df$ego==i & df$alter==j)] <- close[j]
  }
}

# recode
# duration; take midpoint on scale.
df$duration <- ifelse(df$duration=="Minder dan 1 jaar", 0, 
                      ifelse(df$duration=="1 tot 3 jaar", 2,
                             ifelse(df$duration=="4 tot 8 jaar", 6,
                                    ifelse(df$duration=="9 tot 15 jaar", 12,
                                           ifelse(df$duration=="Meer dan 15 jaar", 15, NA)))))
# proximity: same municipality or closer.............
df$proximity <- ifelse(df$proximity=="In de-zelfde buurt" |
                         df$proximity=="In de-zelfde straat" |
                         df$proximity=="In dezelfde ge-meente" |
                         df$proximity=="In het-zelfde huis", 1, 0)

# frequency: at least once a week.
df$frequency <- ifelse(df$frequency=="(Bijna) elke dag" |
                         df$frequency=="1-2 keer per week", 1,0)

df$closeness <- ifelse(df$closeness=="Niet hecht", 1, 
                       ifelse(df$closeness=="Enigszins hecht", 2,
                              ifelse(df$closeness=="Hecht", 3,
                                     ifelse(df$closeness=="Heel erg hecht", 4, NA
                              ))))

# remove last 2 egos (fake responses).
df <- df[-which(df$ego==91 | df$ego==92, arr.ind=T), ]

# save the dataset...
save(df, file = "tie_maintenance.RData")
```

<br>

# tie_creation.RData

<br>

---

## References


